---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

# R workflow for Simple Spatial Surveys Method (S3M) survey in Mozambique

<!-- badges: start -->
[![test S3M workflow](https://github.com/katilingban/mozambique_s3m/actions/workflows/test-s3m-workflow.yaml/badge.svg)](https://github.com/katilingban/mozambique_s3m/actions/workflows/test-s3m-workflow.yaml)
[![run S3M workflow](https://github.com/katilingban/mozambique_s3m/actions/workflows/run-s3m-workflow.yaml/badge.svg)](https://github.com/katilingban/mozambique_s3m/actions/workflows/run-s3m-workflow.yaml)
[![check endline data](https://github.com/katilingban/mozambique-s3m/actions/workflows/check-s3m-data.yaml/badge.svg)](https://github.com/katilingban/mozambique-s3m/actions/workflows/check-s3m-data.yaml)
<!-- badges: end -->

This repository is a [`docker`](https://www.docker.com/get-started)-containerised, [`{targets}`](https://docs.ropensci.org/targets/)-based, [`{renv}`](https://rstudio.github.io/renv/articles/renv.html)-enabled [`R`](https://cran.r-project.org/) workflow developed for the design, data management, data analysis, and reporting of the implementation of Simple Spatial Surveys Method (S3M) survey in Mozambique.

## Spatial sample workfow

```{r spatial_sample_workflow, echo = FALSE, message = FALSE, results = 'asis'}
cat(
  "```mermaid",
  targets::tar_mermaid(
    targets_only = TRUE, 
    names = c(
      cidade_da_beira_sp,
      cidade_da_beira_grid,
      sofala_sp_12,
      sofala_grid_12,
      sofala_sample_12,
      selected_ea_complete
    )
  ),
  "```",
  sep = "\n"
)
```

## Food security indicator set

```{r food_security_workflow, echo = FALSE, message = FALSE, results = 'asis'}
cat(
  "```mermaid",
  targets::tar_mermaid(
    targets_only = TRUE, 
    names = tidyselect::starts_with(
      c("hdds", "fcs", "rcsi", "wdds", "mddw", "lcsi", "fies")
    )
  ),
  "```",
  sep = "\n"
)
```



## Authors

* Mark Myatt
* Ernest Guevarra
