---
title: "Improving nutrition status for under 5 children in Zambezia and Nampula"
subtitle: "Endline Survey Progress and Data Quality Review"
author: 
    - name: Mark Myatt
    - name: Ernest Guevarra
date: '`r Sys.time()`'
output: 
  html_document:
    toc: true
    toc_depth: 3
    self_contained: true
    code_download: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  error = FALSE,
  message = FALSE,
  echo = FALSE
)

suppressPackageStartupMessages(source("packages.R"))
for (f in list.files(here::here("R"), full.names = TRUE)) source (f)

targets::tar_load(
  c(raw_data, respondent_data, respondent_data_clean, child_data, child_data_clean,
    outlier_weight_mother, outlier_height_mother, outlier_muac_mother,
    outlier_muac_mother_cm, outlier_muac_mother_mm, outlier_weight_height_mother, 
    outlier_height_muac_mother, outlier_weight_muac_mother, outlier_weight,
    outlier_height, outlier_muac, outlier_weight_height, outlier_weight_muac, 
    outlier_height_muac, outlier_weight_age, outlier_height_age, 
    outlier_muac_age, outlier_weight_adj, outlier_height_adj, outlier_muac_adj, 
    child_data_zscore, child_data_zscore_adj, skewKurt_wfaz, skewKurt_hfaz, 
    skewKurt_wfhz, dp_weight, dp_height, dp_muac, age_heaping, sex_ratio, 
    age_ratio, table_sp_total, table_sp_children_total, table_sp_date_total,
    endline_sample_list, outlier_summary_univariate_mother, outlier_table_univariate_mother,
    outlier_unique_univariate_mother_total, outlier_summary_bivariate_mother,
    outlier_table_bivariate_mother, outlier_unique_bivariate_mother_total,
    outlier_unique_mother_total, outlier_summary_univariate, 
    outlier_table_univariate, outlier_unique_univariate_total, 
    outlier_summary_univariate_adj, outlier_table_univariate_adj, 
    outlier_unique_univariate_total_adj, outlier_summary_bivariate,
    outlier_table_bivariate, outlier_unique_bivariate_total,
    outlier_unique_total, flag_zscore_total, flag_zscore_prop,
    flag_zscore_adj_total, flag_zscore_adj_prop, whz_mad, age_heaping_class,
    shapiro_wfaz, shapiro_hfaz, shapiro_wfhz
  )
)
```

<style type="text/css">
  body{
  font-size: 14pt;
}
</style>

<br/>

# Summary: The Data Quality Scorecard (DQS)

Following is today's data quality scorecard (DQS) for the endline survey anthropometric dataset.

**Criteria** | **Fail Standard** | **Observed** | **Details**
:--- | :--- |:--- | :---
Outliers | > 1% | Mother data - `r outlier_unique_mother_total$p`; Child data - `r outlier_unique_total$p` | see [2.1. Mother anthropometry] and [2.2. Child anthropometry]
Illegal values | > 1% | Mother data - `r outlier_unique_mother_total$p`; Child data - `r outlier_unique_total$p` | see [2.1. Mother anthropometry] and [2.2. Child anthropometry]
Flagged records | > 5% | `r flag_zscore_prop` | see [2.2.2. Flagged records]
Weight-for-age z-score | Markedly non-normal | Check WAZ Q-Q plot | see [2.2.3. Distribution of anthropometric z-scores and MUAC]
Height-for-age z-score | Markedly non-normal | Check HAZ Q-Q plot | see [2.2.3. Distribution of anthropometric z-scores and MUAC]
Weight-for-height z-score | Markedly non-normal; MAD > 1.2 and MAD < 0.8 | MAD = `r round(whz_mad, 2)` | see [2.2.3. Distribution of anthropometric z-scores and MUAC]; [2.2.4. Median absolute deviation of weight-for-height z-score]
Digit preference - weight | DPS > 12 | `r paste0("DPS = ", dp_weight$dps)` | see [2.2.5. Digit preference]
Digit preference - height | DPS > 12 | `r paste0("DPS = ", dp_height$dps)` | see [2.2.5. Digit preference]
Digit preference - MUAC | DPS > 12 | `r paste0("DPS = ", dp_muac$dps)` | see [2.2.5. Digit preference]
Age heaping | Marked age heaping | `r age_heaping_class` | see [2.2.6. Age heaping]
Sex ratio | p < 0.05 | `r paste0("p = ", round(sex_ratio$p, 4))` | see [2.2.7. Sex ratio]
Age ratio | p < 0.05 | `r paste0("p = ", round(age_ratio$p, 4))` | see [2.2.8. Age ratio]
Age structure | Marked deviation from expected | Check age pyramid and age ratio test | See [2.2.8. Age ratio] and [2.2.9. Age structure]

<br/>
<br/>

# 1. Survey progress

&nbsp;

## 1.1. Cumulative

&nbsp;

### 1.1.1. Number of households surveyed per sampling point identifier as of `r Sys.time()`

```{r, echo = FALSE}
table_sp_total |>
  knitr::kable(
    row.names = FALSE,
    col.names = c("Sampling point identifier", "Number of records"),
    caption = "Number of households interviewed by sampling point ID"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(
    row = nrow(table_sp_total) - 1 , bold = TRUE, font_size = 28
  ) |>
  kableExtra::row_spec(
    row = nrow(table_sp_total), bold = TRUE, color = "red", font_size = 28
  ) |>
  kableExtra::row_spec(
    row = (1:nrow(table_sp_total))[!as.integer(table_sp_total$Var1) %in% 30000:60000],
    bold = TRUE,
    color = "red"
  ) |>
  kableExtra::row_spec(
    row = (1:nrow(table_sp_total))[as.integer(table_sp_total$Var1) %in% 30000:60000 & table_sp_total$Freq < 12],
    bold = TRUE,
    color = "blue"
  ) |>
  kableExtra::row_spec(row = 0, bold = TRUE, align = "center")
```

Sampling point identifiers in <strong><span style="color: red;" >BOLD RED are unrecognised/illegal values</span></strong> for this variable.

Sampling point identifiers in <strong><span style="color: blue;" >BOLD BLUE are sampling point identifiers with less than 12 records</span></strong>.

&nbsp;

### 1.1.2. Number of children surveyed per sampling point identifier at `r Sys.time()`

```{r, echo = FALSE}
table_sp_children_total |>
  knitr::kable(
    row.names = FALSE,
    col.names = c("Sampling point identifier", "Number of records"),
    caption = "Number of children surveyed by sampling point ID"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(
    row = nrow(table_sp_children_total) - 1, bold = TRUE, font_size = 28
  ) |>
    kableExtra::row_spec(
    row = nrow(table_sp_children_total), bold = TRUE, color = "red", font_size = 28
  ) |>
  kableExtra::row_spec(
    row = (1:nrow(table_sp_children_total))[!as.integer(table_sp_children_total$Var1) %in% endline_sample_list$FGH_ID],
    bold = TRUE,
    color = "red"
  ) |>
    kableExtra::row_spec(
    row = (1:nrow(table_sp_children_total))[as.integer(table_sp_children_total$Var1) %in% endline_sample_list$FGH_ID & table_sp_children_total$Freq < 12],
    bold = TRUE,
    color = "blue"
  ) |>
  kableExtra::row_spec(row = 0, bold = TRUE, align = "center")
```

Sampling point identifiers in <strong><span style="color: red;" >BOLD RED are unrecognised/illegal values</span></strong> for this variable.

Sampling point identifiers in <strong><span style="color: blue;" >BOLD BLUE are sampling point identifiers with less than 12 records</span></strong>.

<br/>

## 1.2. By date

```{r, echo = FALSE}
table_sp_date_total |>
  knitr::kable(
    row.names = FALSE,
    caption = "Number of households surveys by sampling point identifier per day"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    font_size = 20,
    position = "center"
  ) |>
  kableExtra::row_spec(row = nrow(table_sp_date_total) - 1, bold = TRUE, font_size = 28) |>
  kableExtra::row_spec(row = nrow(table_sp_date_total), bold = TRUE, color = "red", font_size = 28) |>
  kableExtra::row_spec(
    row = (1:nrow(table_sp_date_total))[!as.integer(row.names(table_sp_date_total)) %in% endline_sample_list$FGH_ID],
    bold = TRUE,
    color = "red"
  ) |>
  kableExtra::row_spec(
    row = (1:nrow(table_sp_date_total))[as.integer(row.names(table_sp_date_total)) %in% endline_sample_list$FGH_ID & table_sp_date_total$`Total records by sampling point identifier per day` < 12],
    bold = TRUE,
    color = "blue"
  ) |>
  kableExtra::row_spec(row = 0, bold = TRUE, align = "center")
```

Sampling point identifiers in <strong><span style="color: red;" >BOLD RED are unrecognised/illegal values</span></strong> for this variable.

Sampling point identifiers in <strong><span style="color: blue;" >BOLD BLUE are sampling point identifiers with less than 12 records</span></strong>.

<br/>

## 1.3. Enumerators recording incorrect sampling point identifier

```{r, echo = FALSE}
x <- data.frame(
  table(
    respondent_data_clean$enumname[!respondent_data_clean$fgh_id %in% endline_sample_list$FGH_ID]
  )
) |>
  (\(x) x[order(x$Freq), ])() |>
  (\(x) rbind(x, data.frame(Var1 = "Total", Freq = sum(x$Freq))))() 

x |>
  knitr::kable(
    row.names = FALSE,
    col.names = c("Enumerator ID", "Number of records with incorrect sampling point identifier")
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    position = "center",
    full_width = FALSE,
    font_size = 20
  ) |>
  kableExtra::row_spec(row = nrow(x), bold = TRUE, font_size = 28)
```

<br/>
<br/>

# 2. Anthropometric data checks

&nbsp;

## 2.1. Mother anthropometry

&nbsp;

### 2.1.1. Check range and legal values

&nbsp;

#### Univariate outliers

```{r, echo = FALSE, fig.align = "center", fig.width = 12, fig.height = 7}
par(mfrow = c(1, 3))
respondent_data_clean |>
  (\(x) boxplot(x$mheight, width = 3, ylab = "cms", main = "Height", cex.main = 2, cex.lab = 1.5))()

respondent_data_clean |>
  (\(x) boxplot(x$mweight, width = 3, ylab = "kgs", main = "Weight", cex.main = 2, cex.lab = 1.5))()
    
respondent_data_clean |>
  (\(x) boxplot(x$mmuac, width = 3, ylab = "cms", main = "MUAC", cex.main = 2, cex.lab = 1.5))()
```

```{r, echo = FALSE}
# n_outlier_weight <- nrow(outlier_weight_mother)
# n_outlier_height <- nrow(outlier_height_mother)
# n_outlier_muac <- nrow(outlier_muac_mother)
# 
# total_unique_univariate <- outlier_weight_mother |>
#   (\(x) rbind(x, outlier_height_mother[!outlier_height_mother$id %in% x$id, ]))() |>
#   (\(x) rbind(x, outlier_muac_mother[!outlier_muac_mother$id %in% x$id, ]))()
# 
# x <- outlier_weight_mother |>
#   (\(x) x[ , c("today", "id", "enumid", "mweight", "mheight", "mmuac")])()
# 
# y <- outlier_height_mother |>
#   (\(x) x[ , c("today", "id", "enumid", "mweight", "mheight", "mmuac")])()
# 
# z <- outlier_muac_mother |>
#   (\(x) x[ , c("today", "id", "enumid", "mweight", "mheight", "mmuac")])()
  
# xyz <- rbind(x, y, z) |>
#   dplyr::mutate(
#     outlier_type = ifelse(id %in% x$id, " weight outlier", ""),
#     outlier_type = ifelse(
#       id %in% y$id, paste0(outlier_type, " height outlier"), outlier_type
#     ),
#     outlier_type = ifelse(
#       id %in% z$id, paste0(outlier_type, " muac outlier"), outlier_type
#     )
#   ) |>
#   (\(x) x[!duplicated(x), ])()

# xyz <- rbind(x, y, z) |>
#   dplyr::mutate(
#     weight_outlier = ifelse(id %in% x$id, "red", "black"),
#     height_outlier = ifelse(id %in% y$id, "red", "black"),
#     muac_outlier = ifelse(id %in% z$id, "red", "black")
#   ) |>
#   (\(x) x[!duplicated(x), ])()

#total_unique_outliers <- nrow(total_unique_univariate)
# total_unique_outliers <- nrow(xyz)
# total_unique_univariate_mother <- nrow(xyz)
# 
# prop_outliers <- total_unique_outliers |>
#   (\(x) x / nrow(respondent_data_clean))() |>
#   scales::percent(accuracy = 0.1)
# 
# x <- c("Weight outlier", "Height outlier", "MUAC outlier") |>
#   data.frame(
#     c(n_outlier_weight, n_outlier_height, n_outlier_muac)
#   )
```

```{r, echo = FALSE}
outlier_summary_univariate_mother |>
  knitr::kable(
    col.names = c("Outlier type", "Number of records"),
    row.names = FALSE,
    caption = "Number of outliers per measurement type"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, bold = TRUE, align = "center")
```

#### A total of **`r outlier_unique_univariate_mother_total$n`** unique univariate outliers were found and are listed below. Potential outlier anthropometric measurements are in <strong><span style="color: red;">BOLD RED</span></strong>.

```{r, echo = FALSE}
outlier_table_univariate_mother |>
  dplyr::mutate(
    mweight = kableExtra::text_spec(
      x = mweight,
      format = "html",
      color = weight_outlier,
      bold = ifelse(weight_outlier == "red", TRUE, FALSE)
    ),
    mheight = kableExtra::text_spec(
      x = mheight,
      format = "html",
      color = height_outlier,
      bold = ifelse(height_outlier == "red", TRUE, FALSE)
    ),
    mmuac = kableExtra::text_spec(
      x = mmuac,
      format = "html",
      color = muac_outlier,
      bold = ifelse(muac_outlier == "red", TRUE, FALSE)
    )
  ) |>
  subset(select = c(today, id, enumid, enumname, mweight, mheight, mmuac)) |>
  knitr::kable(
    row.names = FALSE,
    col.names = c(
      "Survey Date", "Household ID", "Enum ID/Team ID", 
      "Enum Name/Enum ID", "Weight (kgs)", 
      "Height (cms)", "MUAC (cms)"
    ),
    align = "r",
    caption = "Outlier measurements - Mother",
    escape = FALSE
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    position = "center",
    full_width = TRUE,
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, align = "center", bold = TRUE)
```

&nbsp;

#### Bivariate outliers

```{r, echo = FALSE, fig.align = "center", fig.width = 12, fig.height = 7}
par(mfrow = c(1, 3))
with(respondent_data, {
  plot(
    mpeso, maltura,
    pch = ifelse(id %in% outlier_weight_height_mother$id, 20, 1), 
    col = ifelse(id %in% outlier_weight_height_mother$id, "red", "black"),
    xlab = "Weight (kgs)",
    ylab = "Height (cms)",
    main = "Weight (kgs) by Height (cms)", 
    cex.main = 2, cex.lab = 1.5
  )
  plot(
    mpeso, mbraco,
    pch = ifelse(id %in% outlier_weight_muac_mother$id, 20, 1), 
    col = ifelse(id %in% outlier_weight_muac_mother$id, "red", "black"),
    xlab = "Weight (kgs)",
    ylab = "MUAC (cms)",
    main = "Weight (kgs) by MUAC (cms)", 
    cex.main = 2, cex.lab = 1.5
  )
  plot(
    maltura, mbraco,
    pch = ifelse(id %in% outlier_height_muac_mother$id, 20, 1), 
    col = ifelse(id %in% outlier_height_muac_mother$id, "red", "black"),
    xlab = "Height (cms)",
    ylab = "MUAC (cms)",
    main = "Height (cms) by MUAC (cms)", 
    cex.main = 2, cex.lab = 1.5
  )
})
```

```{r, echo = FALSE, eval = TRUE}
# n_outlier_weight_height <- nrow(outlier_weight_height_mother[!is.na(outlier_weight_height_mother$id), ])
# n_outlier_weight_muac <- nrow(outlier_weight_muac_mother[!is.na(outlier_weight_muac_mother$id), ])
# n_outlier_height_muac <- nrow(outlier_height_muac_mother[!is.na(outlier_height_muac_mother$id), ])

# total_unique_bivariate <- outlier_weight_height_mother |>
#   (\(x) rbind(x, outlier_weight_muac_mother[!outlier_weight_muac_mother$id %in% x$id, ]))() |>
#   (\(x) rbind(x, outlier_height_muac_mother[!outlier_height_muac_mother$id %in% x$id, ]))()
# 
# total_unique_outliers <- nrow(total_unique_bivariate[!is.na(total_unique_bivariate$id), ])

# x <- outlier_weight_height_mother |>
#   (\(x) x[ , c("today", "id", "enumid", "mweight", "mheight", "mmuac")])()
# 
# y <- outlier_weight_muac_mother |>
#   (\(x) x[ , c("today", "id", "enumid", "mweight", "mheight", "mmuac")])()
# 
# z <- outlier_height_muac_mother |>
#   (\(x) x[ , c("today", "id", "enumid", "mweight", "mheight", "mmuac")])()
  
# xyz <- rbind(x, y, z) |>
#   dplyr::mutate(
#     outlier_type = ifelse(id %in% x$id, " weight and/or height", ""),
#     outlier_type = ifelse(
#       id %in% y$id, paste0(outlier_type, " weight and/or MUAC"), outlier_type
#     ),
#     outlier_type = ifelse(
#       id %in% z$id, paste0(outlier_type, " height and/or MUAC"), outlier_type
#     )
#   ) |>
#   (\(x) x[!duplicated(x), ])()

# xyz <- rbind(x, y, z) |>
#   dplyr::mutate(
#     weight_outlier = ifelse(id %in% c(x$id, y$id), "red", "black"),
#     height_outlier = ifelse(id %in% c(x$id, z$id), "red", "black"),
#     muac_outlier = ifelse(id %in% c(y$id, z$id), "red", "black")
#   ) |>
#   (\(x) x[!duplicated(x), ])()

# total_unique_outliers <- nrow(xyz)
# total_unique_bivariate_mother <- nrow(xyz)
```


```{r, echo = FALSE}
outlier_summary_bivariate_mother |>
  knitr::kable(
    col.names = c("Outlier type", "Number of records"),
    row.names = FALSE,
    caption = "Number of outliers per bivariate comparison"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, bold = TRUE, align = "center")
```

#### A total of **`r outlier_unique_bivariate_mother_total$n`** unique bivariate outliers were found and listed below. Potential outlier anthropometic measurements are in <strong><span style="color: red;" >BOLD RED</span></strong>.

```{r, echo = FALSE, eval = TRUE}
outlier_table_bivariate_mother |>
  dplyr::mutate(
    mweight = kableExtra::text_spec(
      x = mweight,
      format = "html",
      color = weight_outlier,
      bold = ifelse(weight_outlier == "red", TRUE, FALSE)
    ),
    mheight = kableExtra::text_spec(
      x = mheight,
      format = "html",
      color = height_outlier,
      bold = ifelse(height_outlier == "red", TRUE, FALSE)
    ),
    mmuac = kableExtra::text_spec(
      x = mmuac,
      format = "html",
      color = muac_outlier,
      bold = ifelse(muac_outlier == "red", TRUE, FALSE)
    )
  ) |>
  subset(select = c(today, id, enumid, enumname, mweight, mheight, mmuac)) |>
  knitr::kable(
    row.names = FALSE,
    col.names = c("Survey Date", "Household ID", "Enum ID/Team ID", "Enum Name/Enum ID", 
                  "Weight (kgs)", "Height (cms)", "MUAC (cms)"),
    align = "r",
    caption = "Outliers based on statistical distance",
    escape = FALSE
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped", 
    full_width = FALSE, 
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, align = "center", bold = TRUE)
```

#### A total of **`r outlier_unique_mother_total$n`** unique outliers for mother anthropometric data were found. This is **`r outlier_unique_mother_total$p`** of the total dataset.

<br/>

## 2.2. Child anthropometry

&nbsp;

### 2.2.1. Check range and legal values

&nbsp;

#### Univariate

The boxplots below show the identified outliers for weight, height, and MUAC measurements.

```{r, echo = FALSE, eval = TRUE, fig.align = "center", fig.width = 12, fig.height = 5, fig.cap = "Outlier values for weight, height, and MUAC"}
plot_anthro_outliers(.data = child_data_clean)
```

The number of outliers for each measurement are:

```{r, echo = FALSE, eval = TRUE}
# n_outlier_weight <- nrow(outlier_weight)
# n_outlier_height <- nrow(outlier_height)
# n_outlier_muac <- nrow(outlier_muac)
# 
# total_unique_univariate <- outlier_weight |>
#   (\(x) rbind(x, outlier_height[!outlier_height$id %in% x$id, ]))() |>
#   (\(x) rbind(x, outlier_muac[!outlier_muac$id %in% x$id, ]))()
# 
# x <- outlier_weight |>
#   (\(x) x[ , c("today", "id", "enumid", "cweight", "cheight", "cmuac", "flag")])()
# 
# y <- outlier_height |>
#   (\(x) x[ , c("today", "id", "enumid", "cweight", "cheight", "cmuac", "flag")])()
# 
# z <- outlier_muac |>
#   (\(x) x[ , c("today", "id", "enumid", "cweight", "cheight", "cmuac", "flag")])()
  
# xyz <- rbind(x, y, z) |>
#   dplyr::mutate(
#     outlier_type = ifelse(id %in% x$id, " weight outlier", ""),
#     outlier_type = ifelse(
#       id %in% y$id, paste0(outlier_type, " height outlier"), outlier_type
#     ),
#     outlier_type = ifelse(
#       id %in% z$id, paste0(outlier_type, " muac outlier"), outlier_type
#     )
#   ) |>
#   (\(x) x[!duplicated(x), ])()

# xyz <- rbind(x, y, z) |>
#   dplyr::mutate(
#     weight_outlier = ifelse(id %in% x$id, "red", "black"),
#     height_outlier = ifelse(id %in% y$id, "red", "black"),
#     muac_outlier = ifelse(id %in% z$id, "red", "black")
#   ) |>
#   (\(x) x[!duplicated(x), ])()


#total_unique_outliers <- nrow(total_unique_univariate)
#total_unique_outliers <- nrow(xyz)
```


```{r, echo = FALSE}
outlier_summary_univariate |>
  knitr::kable(
    col.names = c("Outlier type", "Number of records"),
    row.names = FALSE,
    caption = "Number of outliers per measurement type"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, bold = TRUE, align = "center")
```

#### A total of **`r outlier_unique_univariate_total$n`** unique univariate outliers were found and listed below. Potential outlier anthropometric measurements are in <strong><span style="color: red;">BOLD RED</span></strong>.

```{r, echo = FALSE, eval = TRUE}
outlier_table_univariate |>
  dplyr::mutate(
    cweight = kableExtra::text_spec(
      x = cweight,
      format = "html",
      color = weight_outlier,
      bold = ifelse(weight_outlier == "red", TRUE, FALSE)
    ),
    cheight = kableExtra::text_spec(
      x = cheight,
      format = "html",
      color = height_outlier,
      bold = ifelse(height_outlier == "red", TRUE, FALSE)
    ),
    cmuac = kableExtra::text_spec(
      x = cmuac,
      format = "html",
      color = muac_outlier,
      bold = ifelse(muac_outlier == "red", TRUE, FALSE)
    ),
    flag = ifelse(flag == 1, "YES", "NO")
  ) |>
  subset(select = c(today, id, enumid, enumname, cweight, cheight, cmuac, age_months, flag)) |>
  knitr::kable(
    row.names = FALSE,
    col.names = c("Survey Date", "Household ID", "Enum ID/Team ID", "Enum Name/Enum ID", 
                  "Weight (kgs)", "Height (cms)", "MUAC (cms)", "Age (months)", "Flagged in ODK"),
    align = "r",
    caption = "Outlier measurements - children",
    escape = FALSE
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped", 
    full_width = FALSE, 
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, align = "center", bold = TRUE)
```

When measurements are adjusted using the re-measured values, we get:

```{r, echo = FALSE, eval = TRUE}
# n_outlier_weight <- nrow(outlier_weight_adj)
# n_outlier_height <- nrow(outlier_height_adj)
# n_outlier_muac <- nrow(outlier_muac_adj)
# 
# x <- outlier_weight_adj |>
#   (\(x) x[ , c("today", "id", "enumid", "cweight1", "cheight1", "cmuac1", "flag")])()
# 
# y <- outlier_height_adj |>
#   (\(x) x[ , c("today", "id", "enumid", "cweight1", "cheight1", "cmuac1", "flag")])()
# 
# z <- outlier_muac_adj |>
#   (\(x) x[ , c("today", "id", "enumid", "cweight1", "cheight1", "cmuac1", "flag")])()
  
# xyz <- rbind(x, y, z) |>
#   dplyr::mutate(
#     outlier_type = ifelse(id %in% x$id, " weight outlier", ""),
#     outlier_type = ifelse(
#       id %in% y$id, paste0(outlier_type, " height outlier"), outlier_type
#     ),
#     outlier_type = ifelse(
#       id %in% z$id, paste0(outlier_type, " muac outlier"), outlier_type
#     )
#   ) |>
#   (\(x) x[!duplicated(x), ])()

# xyz <- rbind(x, y, z) |>
#   dplyr::mutate(
#     weight_outlier = ifelse(id %in% x$id, "red", "black"),
#     height_outlier = ifelse(id %in% y$id, "red", "black"),
#     muac_outlier = ifelse(id %in% z$id, "red", "black")
#   ) |>
#   (\(x) x[!duplicated(x), ])()

#total_unique_outliers <- nrow(total_unique_univariate)
# total_unique_univariate <- outlier_weight_adj |>
#   (\(x) rbind(x, outlier_height_adj[!outlier_height_adj$id %in% x$id, ]))() |>
#   (\(x) rbind(x, outlier_muac_adj[!outlier_muac_adj$id %in% x$id, ]))()
#total_unique_univariate <- nrow(xyz)
#total_unique_outliers <- nrow(xyz)
```

```{r, echo = FALSE}
outlier_summary_univariate_adj |>
  knitr::kable(
    col.names = c("Outlier type", "Number of records"),
    row.names = FALSE,
    caption = "Number of outliers per measurement type"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, align = "center", bold = TRUE)
```

#### A total of **`r outlier_unique_univariate_total_adj$n`** unique outliers were found and listed below. Potential outlier anthropometric measurements are in <strong><span style="color: red;" >BOLD RED</span></strong>.

```{r, echo = FALSE, eval = TRUE}
# xyz |>
outlier_table_univariate_adj |>
  dplyr::mutate(
    cweight1 = kableExtra::text_spec(
      x = cweight1,
      format = "html",
      color = weight_outlier,
      bold = ifelse(weight_outlier == "red", TRUE, FALSE)
    ),
    cheight1 = kableExtra::text_spec(
      x = cheight1,
      format = "html",
      color = height_outlier,
      bold = ifelse(height_outlier == "red", TRUE, FALSE)
    ),
    cmuac1 = kableExtra::text_spec(
      x = cmuac1,
      format = "html",
      color = muac_outlier,
      bold = ifelse(muac_outlier == "red", TRUE, FALSE)
    ),
    flag = ifelse(flag == 1, "YES", "NO")
  ) |>
  subset(select = c(today, id, enumid, enumname, cweight1, cheight1, cmuac1, age_months, flag)) |>
  knitr::kable(
    row.names = FALSE,
    col.names = c("Survey Date", "Household ID", "Enum ID/Team ID", "Enum Name/Enum ID", 
                  "Weight (kgs)", "Height (cms)", "MUAC (cms)", "Age (months)", "Flagged in ODK"),
    align = "r",
    caption = "Outlier measurements (adjusted) - children",
    escape = FALSE
  )|>
  kableExtra::kable_styling(
    bootstrap_options = "striped", 
    full_width = TRUE, 
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, align = "center", bold = TRUE)
```

&nbsp;

#### Bivariate outliers

The scatterplots below identify various bivariate outliers.

```{r, echo = FALSE, eval = TRUE, fig.align = "center", fig.width = 12, fig.height = 5, fig.cap = "Bivariate outliers based on statistical distance"}
child_data_clean |>
plot_anthro_bivariate(
  outlier_weight_height, 
  outlier_weight_muac, 
  outlier_height_muac, 
  outlier_weight_age, 
  outlier_height_age, 
  outlier_muac_age
)
```

Following are the number of outliers identified per bivariate comparison.

```{r, echo = FALSE, eval = TRUE}
# n_outlier_weight_height <- nrow(outlier_weight_height)
# n_outlier_weight_muac <- nrow(outlier_weight_muac)
# n_outlier_height_muac <- nrow(outlier_height_muac)
# n_outlier_weight_age <- nrow(outlier_weight_age)
# n_outlier_height_age <- nrow(outlier_height_age)
# n_outlier_muac_age <- nrow(outlier_muac_age)
# 
# x <- outlier_weight_height |>
#   (\(x) x[ , c("today", "id", "enumid", "cweight", "cheight", "cmuac", "age_months", "flag")])()
# 
# y <- outlier_weight_muac |>
#   (\(x) x[ , c("today", "id", "enumid", "cweight", "cheight", "cmuac", "age_months", "flag")])()
# 
# z <- outlier_height_muac |>
#   (\(x) x[ , c("today", "id", "enumid", "cweight", "cheight", "cmuac", "age_months", "flag")])()
# 
# a <- outlier_weight_age |>
#   (\(x) x[ , c("today", "id", "enumid", "cweight", "cheight", "cmuac", "age_months", "flag")])()
# 
# b <- outlier_height_age |>
#   (\(x) x[ , c("today", "id", "enumid", "cweight", "cheight", "cmuac", "age_months", "flag")])()
#   
# c <- outlier_muac_age |>
#   (\(x) x[ , c("today", "id", "enumid", "cweight", "cheight", "cmuac", "age_months", "flag")])()

# xyzabc <- rbind(x, y, z, a, b, c) |>
#   dplyr::mutate(
#     outlier_type = ifelse(id %in% x$id, " weight and/or height", ""),
#     outlier_type = ifelse(
#       id %in% y$id, paste0(outlier_type, " weight and/or MUAC"), outlier_type
#     ),
#     outlier_type = ifelse(
#       id %in% z$id, paste0(outlier_type, " height and/or MUAC"), outlier_type
#     ),
#     outlier_type = ifelse(
#       id %in% a$id, paste0(outlier_type, " weight and/or age"), outlier_type
#     ),
#     outlier_type = ifelse(
#       id %in% b$id, paste0(outlier_type, " height and/or age"), outlier_type
#     ),
#     outlier_type = ifelse(
#       id %in% c$id, paste0(outlier_type, " muac and/or age"), outlier_type
#     ),
#   ) |>
#   (\(x) x[!duplicated(x), ])()

# xyzabc <- rbind(x, y, z, a, b, c) |>
#   dplyr::mutate(
#     weight_outlier = ifelse(id %in% c(x$id, y$id, a$id), "red", "black"),
#     height_outlier = ifelse(id %in% c(x$id, z$id, b$id), "red", "black"),
#     muac_outlier = ifelse(id %in% c(y$id, z$id, c$id), "red", "black"),
#     age_outlier = ifelse(id %in% c(a$id, b$id, c$id), "red", "black")
#   ) |>
#   (\(x) x[!duplicated(x), ])()

#total_unique_outliers <- nrow(total_unique_bivariate)
# total_unique_bivariate <- outlier_weight_height |>
#   (\(x) rbind(x, outlier_weight_muac[!outlier_weight_muac$id %in% x$id, ]))() |>
#   (\(x) rbind(x, outlier_height_muac[!outlier_height_muac$id %in% x$id, ]))() |>
#   (\(x) rbind(x, outlier_weight_age[!outlier_weight_age$id %in% x$id, ]))() |>
#   (\(x) rbind(x, outlier_height_age[!outlier_height_age$id %in% x$id, ]))() |>
#   (\(x) rbind(x, outlier_muac_age[!outlier_muac_age$id %in% x$id, ]))()
#total_unique_bivariate <- nrow(xyzabc)
#total_unique_outliers <- nrow(xyzabc)
```

```{r, echo = FALSE}
outlier_summary_bivariate |>
  knitr::kable(
    col.names = c("Outlier type", "Number of records"),
    row.names = FALSE,
    caption = "Number of outliers per bivariate comparison"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, align = "center", bold = TRUE)
```

#### A total of **`r outlier_unique_bivariate_total$n`** unique bivariate outliers are found and listed below. Potential outlier anthropometric measurements are in <strong><span style="color: red;">BOLD RED</span></strong>.

```{r, echo = FALSE, eval = TRUE}
# xyzabc |>
#   #subset(select = c(id, enumid, cweight, cheight, cmuac, age_months)) |>
#   knitr::kable(
#     row.names = FALSE,
#     col.names = c("Survey Date", "Household ID", "Enumerator ID", "Weight (kgs)", "Height (cms)", "MUAC (cms)", "Age (months)", "Flagged in Survey", "Outlier Type"),
#     caption = "Bivariate outliers based on statistical distance"
#   ) |>
#   kableExtra::kable_styling(
#     bootstrap_options = "striped", 
#     full_width = TRUE, 
#     position = "center",
#     font_size = 20
#   ) |>
#   kableExtra::row_spec(row = 0, align = "center")

outlier_table_bivariate |>
  dplyr::mutate(
    cweight = kableExtra::text_spec(
      x = cweight,
      format = "html",
      color = weight_outlier,
      bold = ifelse(weight_outlier == "red", TRUE, FALSE)
    ),
    cheight = kableExtra::text_spec(
      x = cheight,
      format = "html",
      color = height_outlier,
      bold = ifelse(height_outlier == "red", TRUE, FALSE)
    ),
    cmuac = kableExtra::text_spec(
      x = cmuac,
      format = "html",
      color = muac_outlier,
      bold = ifelse(muac_outlier == "red", TRUE, FALSE)
    ),
    flag = ifelse(flag == 1, "YES", "NO")
  )|>
  subset(select = c(today, id, enumid, enumname, cweight, cheight, cmuac, age_months, flag)) |>
  knitr::kable(
    row.names = FALSE,
    col.names = c("Survey Date", "Household ID", "Enum ID/Team ID", "Enum Name/Enum ID", "Weight (kgs)", "Height (cms)", "MUAC (cms)", "Age (months)", "Flagged in ODK"),
    align = "r",
    caption = "Bivariate outliers based on statistical distance",
    escape = FALSE
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped", 
    full_width = TRUE, 
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, align = "center")
```

#### A total of **`r outlier_unique_total$n` outliers** were found. This is **`r outlier_unique_total$p`** of the full child anthropometric dataset.

&nbsp;

### 2.2.2. Flagged records

The anthropometric z-scores are calculated using the [`{zscorer}`](https://nutriverse.io/zscorer). Values are then assessed based on the WHO flagging criteria and problematic values are flagged. For this, we only use the data from children 6-59 months old and we first calculate z-score using the first measurements.

This produces an updated anthropometric dataset that now includes calculated anthropometric z-scores (weight-for-age, height-for-age, and weight-for-height) and identifies flagged values based on WHO flagging criteria and indicates which anthropometric measurement is potentially problematic.

Following are the flagged records in the anthropometric dataset. Anthropometric measurements with potential issues are in <strong><span style="color: red;" >BOLD RED</span></strong>.

```{r, eval = TRUE}
child_data_zscore |>
  dplyr::filter(
    flag_zscore != 0
    #flag_description != "No flagged measurements"#,
    #(cpeso != 0 | caltura != 0 | cbraco != 0)
  ) |>
  dplyr::mutate(
    weight_flag = ifelse(flag_zscore %in% c(2, 4, 6, 7), "red", "black"),
    height_flag = ifelse(flag_zscore %in% c(1, 2, 3, 7), "red", "black"),
    age_flag = ifelse(flag_zscore %in% c(1, 4, 5, 7), "red", "black"),
    cweight = kableExtra::text_spec(
      x = cweight,
      format = "html",
      color = weight_flag,
      bold = ifelse(weight_flag == "red", TRUE, FALSE)
    ),
    cheight = kableExtra::text_spec(
      x = cheight,
      format = "html",
      color = height_flag,
      bold = ifelse(height_flag == "red", TRUE, FALSE)
    ),
    age_months = kableExtra::text_spec(
      x = floor(age_months),
      format = "html",
      color = age_flag,
      bold = ifelse(age_flag == "red", TRUE, FALSE)
    ),
    flag = ifelse(flag == 1, "YES", "NO")
  ) |>
  subset(select = c(today, id, enumid, flag_description, flag, cweight, cheight, age_months)) |>
  #(\(x) x[ , c("today", "id", "enumid", "flag_description", "flag", "cweight", "cheight", "age_months")])()|>
  knitr::kable(
    row.names = FALSE,
    col.names = c(
      "Survey Date", "Household ID", "Enumerator ID", "Flag Description", "Flagged in ODK", "Weight (kgs)", "Height (cms)", "Age (months)"
    ),
    caption = "Records with flagged anthropometric measurements based on WHO flagging criteria",
    escape = FALSE
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = TRUE,
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, align = "center")
```

A total of **`r flag_zscore_total`** records are identified. This is **`r flag_zscore_prop`** of the total records in the child anthropometric dataset.

Following are the flagged records in the anthropometric dataset after adjusting the measurements. Anthropometric measurements with potential issues are in <strong><span style="color: red;" >BOLD RED</span></strong>.

```{r, eval = TRUE}
child_data_zscore_adj |>
  dplyr::filter(
    flag_zscore != 0,
    #flag_description != "No flagged measurements",
    #(cpeso != 0 | caltura != 0 | cbraco != 0)
  ) |>
  dplyr::mutate(
    weight_flag = ifelse(flag_zscore %in% c(2, 4, 6, 7), "red", "black"),
    height_flag = ifelse(flag_zscore %in% c(1, 2, 3, 7), "red", "black"),
    age_flag = ifelse(flag_zscore %in% c(1, 4, 5, 7), "red", "black"),
    cweight = kableExtra::text_spec(
      x = cweight,
      format = "html",
      color = weight_flag,
      bold = ifelse(weight_flag == "red", TRUE, FALSE)
    ),
    cheight = kableExtra::text_spec(
      x = cheight,
      format = "html",
      color = height_flag,
      bold = ifelse(height_flag == "red", TRUE, FALSE)
    ),
    age_months = kableExtra::text_spec(
      x = round(age_months),
      format = "html",
      color = age_flag,
      bold = ifelse(age_flag == "red", TRUE, FALSE)
    ),
    flag = ifelse(flag == 1, "YES", "NO")
  ) |>
  subset(select = c(today, id, enumid, flag_description, flag, cweight, cheight, age_months)) |>  
  #(\(x) x[ , c("id", "enumid", "flag_description", "flag", "cweight1", "cheight1", "age_months")])()|>
  knitr::kable(
    row.names = FALSE,
    col.names = c("Survey Date", "Household ID", "Enumerator ID", "Flag Description", "Flagged in ODK", "Weight (kgs)", "Height (cms)", "Age (months)"
    ),
    caption = "Records with flagged anthropometric measurements based on WHO flagging criteria after measurement adjustment",
    escape = FALSE
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = TRUE,
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, align = "center")
```

A total of **`r flag_zscore_adj_total` child records** were flagged. This is **`r flag_zscore_adj_prop`** of the total records in the child anthropometric dataset.

&nbsp;

### 2.2.3. Distribution of anthropometric z-scores and MUAC

Removing outliers and flagged anthropometric measurements, we observe the distribution of the anthropometric z-scores and MUAC as follows:

```{r, echo = FALSE, eval = TRUE, fig.align = "center", fig.width = 12, fig.height = 5, fig.cap = "Distribution of anthropometric z-score values and MUAC"}
withr::with_par(
  new = list(par(mfrow = c(1, 4))),
  {
    with(
      child_data_zscore |>
        dplyr::filter(!id %in% c(outlier_table_univariate$id, outlier_table_bivariate$id) | flag_zscore == 0),
      {
        histNormal(wfaz, main = "Weight-for-age z-score", xlab = "z-score")
        histNormal(hfaz, main = "Height-for-age z-score", xlab = "z-score")
        histNormal(wfhz, main = "Weight-for-height z-score", xlab = "z-score")
        histNormal(cmuac, main = "MUAC", xlab = "cms")
      }
    )
  }
)
```

```{r, echo = FALSE, eval = TRUE, fig.align = "center", fig.width = 12, fig.height = 5, fig.cap = "Quantile-quantile plots of anthropometric z-score values and MUAC"}
withr::with_par(
  new = list(par(mfrow = c(1, 4))),
  {
    with(
      child_data_zscore |>
        dplyr::filter(!id %in% c(outlier_table_univariate$id, outlier_table_bivariate$id) | flag_zscore == 0),
      {
        qqNormalPlot(wfaz)
        qqNormalPlot(hfaz)
        qqNormalPlot(wfhz)
        qqNormalPlot(cmuac)
      }
    )
  }
)
```

&nbsp;

#### **Skewness and Kurtosis**

Checking for skewness and kurtosis on child anthropometric data, the following are observed:

**Skewness and kurtosis of weight-for-age z-score**

```{r, echo = FALSE, eval = TRUE}
skewKurt_wfaz
```

**Skewness and kurtosis of height-for-age z-score**

```{r, echo = FALSE, eval = TRUE}
skewKurt_hfaz
```

**Skewness and kurtosis of weight-for-height z-score**

```{r, echo = FALSE, eval = TRUE}
skewKurt_wfhz
```

Checking for skewness and kurtosis on child anthropometric data where outliers and flagged values have been removed, the following are observed:

**Skewness and kurtosis of weight-for-age z-score - without outliers and flagged values**

```{r, echo = FALSE, eval = TRUE}
skewKurt_wfaz_adj <- child_data_zscore |>
    dplyr::filter(!id %in% c(outlier_table_univariate$id, outlier_table_bivariate$id) | flag_zscore == 0) |>
    (\(x) skewKurt(x$wfaz))()

skewKurt_wfaz_adj
```

**Skewness and kurtosis of height-for-age z-score - without outliers and flagged values**

```{r, echo = FALSE, eval = TRUE}
skewKurt_hfaz_adj <- child_data_zscore |>
    dplyr::filter(!id %in% c(outlier_table_univariate$id, outlier_table_bivariate$id) | flag_zscore == 0) |>
    (\(x) skewKurt(x$hfaz))()

skewKurt_hfaz_adj
```

**Skewness and kurtosis of weight-for-height z-score - without outliers and flagged values**

```{r, echo = FALSE, eval = TRUE}
skewKurt_wfhz_adj <- child_data_zscore |>
    dplyr::filter(!id %in% c(outlier_table_univariate$id, outlier_table_bivariate$id) | flag_zscore == 0) |>
    (\(x) skewKurt(x$wfhz))()

skewKurt_wfhz_adj
```

&nbsp;

### 2.2.4. Median absolute deviation of weight-for-height z-score

```{r, echo = FALSE, eval = TRUE}
if (whz_mad >= 0.8 & whz_mad <= 1.2) {
 mad_result <- "within the 0.8 to 1.2 range recommended."
} else {
  mad_result <- "NOT within the 0.8 to 1.2 range recommended."
}
```

The median absolute deviation (MAD) for weight-for-height z-score is **`r whz_mad`**. This is **`r mad_result`**.

&nbsp;

### 2.2.5. Digit preference

```{r, echo = FALSE, eval = TRUE, fig.align = "center", fig.width = 12, fig.height = 5, fig.cap = "Digit preference scores and plots for weight, height and MUAC"}
withr::with_par(
  new = list(par(mfrow = c(1, 3))),
  {
    with(child_data_zscore,
      {
        plot(dp_weight, cex.main = 2, cex.lab = 1.5)
        plot(dp_height, cex.main = 2, cex.lab = 1.5)
        plot(dp_muac, cex.main = 2, cex.lab = 1.5)
      }     
    )
  }
)
```

The **digit preference score for weight** is **`r dp_weight$dps`**. This digit preference score is **`r dp_weight$dpsClass`**.

The **digit preference score for height** is **`r dp_height$dps`**. This digit preference score is **`r dp_height$dpsClass`**.

The **digit preference score for MUAC** is **`r dp_muac$dps`**. This digit preference score is **`r dp_muac$dpsClass`**.

&nbsp;

### 2.2.6. Age heaping

```{r, echo = FALSE, eval = TRUE, fig.align = "center", fig.width = 8, fig.cap = "Plot assessing age heaping in the anthropometric dataset"}
plot(age_heaping)
```

```{r, echo = FALSE, eval = TRUE}
age_heaping

if (age_heaping$p < 0.05) {
  age_heaping_result <- "significant age heaping at whole years"
} else {
  age_heaping_result <- "no significant age heaping at whole years"
}
```

There is **`r age_heaping_result`** in the child anthropometric dataset.

&nbsp;

### 2.2.7. Sex ratio

The sex ratio in the anthropometric dataset is compared against the expected sex ratio of children under 5 years old in Mozambique which is 1.03 males for every female (from the [United States Census Bureau’s International Data Base](https://www.census.gov/data-tools/demo/idb/#/pop?COUNTRY_YEAR=2018&COUNTRY_YR_ANIM=2018&FIPS_SINGLE=MZ&menu=popViz&POP_YEARS=2018&quickReports=OVW&popPages=BYAGE&FIPS=MZ&ageGroup=5Y)).

```{r, echo = FALSE, eval = TRUE}
sex_ratio
```

```{r, echo = FALSE}
if (sex_ratio$p < 0.05) {
  sex_ratio_result <- "significantly different from the ratio of boys and girls in the general population"
} else {
  sex_ratio_result <- "not significantly different from the ratio of boys and girls in the general population"
}
```

The ratio of boys and girls in the data is **`r sex_ratio_result`** in Mozambique.

&nbsp;

### 2.2.8. Age ratio

```{r, echo = FALSE, eval = TRUE}
age_ratio
#age_ratio_by_sex
```

```{r, echo = FALSE}
if (age_ratio$p < 0.05) {
  age_ratio_result <- "significantly different from the expected age ratio of 0.85"
} else {
  age_ratio_result <- "not significantly different from the expected age ratio of 0.85"
}
```

The age ratio in the child anthropometric dataset is **`r age_ratio_result`**.

&nbsp;

### 2.2.9. Age structure

```{r, echo = FALSE, eval = TRUE, fig.align = "center", fig.width = 8, fig.height = 10, fig.cap = "Age structure of the under 5 sample"}
plot_age_structure(.data = child_data)
```

<br/>
<br/>

<!---

# 3. Summary: The Data Quality Scorecard (DQS)

Following is today's data quality scorecard (DQS) for the endline survey anthropometric dataset.

```{r, echo = FALSE, eval = TRUE}
criteria <- c("Outliers", "Illegal values", "Flagged records", "Weight-for-age z-score", "Height-for-age z-score", "Weight-for-age z-score", "Digit preference - weight", "Digit preference - height", "Digit preference - MUAC", "Age heaping", "Sex ratio", "Age ratio", "Age structure")

fail_standard <- c("> 1%", "> 1%", "> 5%", "Markedly non-normal", "Markedly non-normal", "Markedly non-normal; MAD > 1.2 and MAD < 0.8", "DPS > 12", "DPS > 12", "DPS > 12", "Marked age heaping", "p < 0.05", "p < 0.05", "Marked deviation from expected")

observed <- c(
  paste0("Mother data - ", outlier_unique_mother_total$p, "; Child data - ", outlier_unique_total$p), 
  paste0("Mother data - ", outlier_unique_mother_total$p, "; Child data - ", outlier_unique_total$p), 
  flag_zscore_prop, 
  "See WAZ Q-Q plot", 
  "See HAZ Q-Q plot", 
  paste0("See WHZ Q-Q plot; MAD = ", whz_mad), 
  paste0("DPS = ", dp_weight$dps), 
  paste0("DPS = ", dp_height$dps), 
  paste0("DPS = ", dp_muac$dps), 
  ifelse(
    age_heaping$p < 0.05, 
    paste0("Marked age heaping at whole years (p = ", round(age_heaping$p, 4), ")"),
    paste0("No marked age heaping at whole years (p = ", round(age_heaping$p, 4), ")")
  ),
  paste0("p = ", round(sex_ratio$p, 4)), 
  paste0("p = ", round(age_ratio$p, 4)), 
  "See age pyramid and age ratio test")

classification <- c("Fail", "Pass", "Pass", "Pass", "Fail", "Pass", "Pass", "Pass", "Pass", "Fail", "Pass", "Fail", "Pass")

#dqs <- data.frame(criteria, fail_standard, observed, classification) 
dqs <- data.frame(criteria, fail_standard, observed) 

dqs |>
  knitr::kable(
    caption = "Data Quality Scorecard",
    col.names = c("Criteria", "Fail Standard", "Observed"),
    row.names = FALSE
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = TRUE,
    position = "center",
    font_size = 16
  )
```
--->

<br/>
<br/>