---
title: "Sofala Simple Spatial Survey Method (S3M)"
subtitle: "Data Quality"
author: 
    - name: Mark Myatt
    - name: Ernest Guevarra
date: '`r Sys.time()`'
output: 
  html_document:
    toc: true
    toc_depth: 3
    self_contained: true
    code_download: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  error = FALSE,
  message = FALSE,
  echo = FALSE
)

suppressPackageStartupMessages(source("packages.R"))
for (f in list.files(here::here("R"), full.names = TRUE)) source (f)

targets::tar_load(
  c(raw_data, raw_data_clean, selected_ea_complete, complete_ea_sf,
    outlier_weight_mother, outlier_height_mother, outlier_muac_mother,
    outlier_muac_mother_cm, outlier_muac_mother_mm, outlier_weight_height_mother, 
    outlier_height_muac_mother, outlier_weight_muac_mother, outlier_weight,
    outlier_height, outlier_muac, outlier_weight_height, outlier_weight_muac, 
    outlier_height_muac, outlier_weight_age, outlier_height_age, 
    outlier_muac_age, outlier_weight_adj, outlier_height_adj, outlier_muac_adj, 
    child_data_zscore, child_data_zscore_adj, skewKurt_wfaz, skewKurt_hfaz, 
    skewKurt_wfhz, dp_weight, dp_height, dp_muac, age_heaping, sex_ratio, 
    age_ratio, table_sp_total, table_sp_children_total, table_sp_date_total,
    endline_sample_list, outlier_summary_univariate_mother, outlier_table_univariate_mother,
    outlier_unique_univariate_mother_total, outlier_summary_bivariate_mother,
    outlier_table_bivariate_mother, outlier_unique_bivariate_mother_total,
    outlier_unique_mother_total, outlier_summary_univariate, 
    outlier_table_univariate, outlier_unique_univariate_total, 
    outlier_summary_univariate_adj, outlier_table_univariate_adj, 
    outlier_unique_univariate_total_adj, outlier_summary_bivariate,
    outlier_table_bivariate, outlier_unique_bivariate_total,
    outlier_unique_total, flag_zscore_total, flag_zscore_prop,
    flag_zscore_adj_total, flag_zscore_adj_prop, whz_mad, age_heaping_class,
    shapiro_wfaz, shapiro_hfaz, shapiro_wfhz,
    skew_wfaz_class, kurt_wfaz_class, skew_hfaz_class, kurt_hfaz_class,
    skew_wfhz_class, kurt_wfhz_class, 
    skewKurt_wfaz_adj, skewKurt_hfaz_adj, skewKurt_wfhz_adj,
    skew_wfaz_adj_class, kurt_wfaz_adj_class, 
    skew_hfaz_adj_class, kurt_hfaz_adj_class, skew_wfhz_adj_class, kurt_wfhz_adj_class
  )
)
```

<style type="text/css">
  body{
  font-size: 14pt;
}
</style>

<br/>

# 1. Summary: The Data Quality Scorecard (DQS)

Following is today's data quality scorecard (DQS) for the endline survey anthropometric dataset.

**Criteria** | **Fail Standard** | **Observed** | **Details**
:--- | :--- |:--- | :---
Outliers | > 1% | Mother data - `r outlier_unique_mother_total$p`; Child data - `r outlier_unique_total$p` | see [2.1. Mother anthropometry] and [2.2. Child anthropometry]
Illegal values | > 1% | Mother data - `r outlier_unique_mother_total$p`; Child data - `r outlier_unique_total$p` | see [2.1. Mother anthropometry] and [2.2. Child anthropometry]
Flagged records | > 5% | `r flag_zscore_prop` | see [2.2.2. Flagged records]
Weight-for-age z-score | Markedly non-normal | Check WAZ Q-Q plot; Skewness = `r paste0(format(round(skewKurt_wfaz_adj$s), scientific = FALSE), " (", skew_wfaz_adj_class, ")")`; Kurtosis = `r paste0(format(round(skewKurt_wfaz_adj$k), scientific = FALSE), " (", kurt_wfaz_adj_class, ")")` | see [2.2.3. Distribution of anthropometric z-scores and MUAC]
Height-for-age z-score | Markedly non-normal | Check HAZ Q-Q plot; Skewness = `r paste0(format(round(skewKurt_hfaz_adj$s), scientific = FALSE), " (", skew_hfaz_adj_class, ")")`; Kurtosis = `r paste0(format(round(skewKurt_hfaz_adj$k), scientific = FALSE), " (", kurt_hfaz_adj_class, ")")` | see [2.2.3. Distribution of anthropometric z-scores and MUAC]
Weight-for-height z-score | Markedly non-normal; MAD > 1.2 or MAD < 0.8 | Check WHZ Q-Q plot; Skewness = `r paste0(format(round(skewKurt_wfhz_adj$s), scientific = FALSE), " (", skew_wfhz_adj_class, ")")`; Kurtosis = `r paste0(format(round(skewKurt_wfhz_adj$k), scientific = FALSE), " (", kurt_wfhz_adj_class, ")")`; MAD = `r round(whz_mad, 2)` | see [2.2.3. Distribution of anthropometric z-scores and MUAC]; [2.2.4. Median absolute deviation of weight-for-height z-score]
Digit preference - weight | DPS > 12 | `r paste0("DPS = ", dp_weight$dps)` | see [2.2.5. Digit preference]
Digit preference - height | DPS > 12 | `r paste0("DPS = ", dp_height$dps)` | see [2.2.5. Digit preference]
Digit preference - MUAC | DPS > 12 | `r paste0("DPS = ", dp_muac$dps)` | see [2.2.5. Digit preference]
Age heaping | Marked age heaping | `r age_heaping_class` | see [2.2.6. Age heaping]
Sex ratio | p < 0.05 | `r paste0("p = ", round(sex_ratio$p, 4))` | see [2.2.7. Sex ratio]
Age ratio | p < 0.05 | `r paste0("p = ", round(age_ratio$p, 4))` | see [2.2.8. Age ratio]
Age structure | Marked deviation from expected | Check age pyramid and age ratio test | See [2.2.8. Age ratio] and [2.2.9. Age structure]

<br/>
<br/>

# 2. Anthropometric data checks

&nbsp;

## 2.1. Mother anthropometry

&nbsp;

### 2.1.1. Check range and legal values

&nbsp;

#### Univariate outliers

```{r, echo = FALSE, fig.align = "center", fig.width = 12, fig.height = 7}
par(mfrow = c(1, 3))
raw_data_clean |>
  (\(x) boxplot(x$mweight, width = 3, ylab = "kgs", main = "Weight", cex.main = 2, cex.lab = 1.5))()

raw_data_clean |>
  (\(x) boxplot(x$mheight, width = 3, ylab = "cms", main = "Height", cex.main = 2, cex.lab = 1.5))()
    
raw_data_clean |>
  (\(x) boxplot(x$mmuac, width = 3, ylab = "cms", main = "MUAC", cex.main = 2, cex.lab = 1.5))()
```

```{r, echo = FALSE}
outlier_summary_univariate_mother |>
  knitr::kable(
    col.names = c("Outlier type", "Number of records"),
    row.names = FALSE,
    caption = "Number of outliers per measurement type"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, bold = TRUE, align = "center")
```

#### A total of **`r outlier_unique_univariate_mother_total$n`** unique univariate outliers were found and are listed below. Potential outlier anthropometric measurements are in <strong><span style="color: red;">BOLD RED</span></strong>.

```{r, echo = FALSE}
outlier_table_univariate_mother |>
  dplyr::mutate(
    mweight = kableExtra::text_spec(
      x = mweight,
      format = "html",
      color = weight_outlier,
      bold = ifelse(weight_outlier == "red", TRUE, FALSE)
    ),
    mheight = kableExtra::text_spec(
      x = mheight,
      format = "html",
      color = height_outlier,
      bold = ifelse(height_outlier == "red", TRUE, FALSE)
    ),
    mmuac = kableExtra::text_spec(
      x = mmuac,
      format = "html",
      color = muac_outlier,
      bold = ifelse(muac_outlier == "red", TRUE, FALSE)
    )
  ) |>
  subset(select = c(today, id, ad2, ad3, mweight, mheight, mmuac)) |>
  knitr::kable(
    row.names = FALSE,
    col.names = c(
      "Survey Date", "Record ID", "Survey Team", 
      "Enum Code", "Weight (kgs)", 
      "Height (cms)", "MUAC (cms)"
    ),
    align = "r",
    caption = "Outlier measurements - Mother",
    escape = FALSE
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    position = "center",
    full_width = TRUE,
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, align = "center", bold = TRUE)
```

&nbsp;

#### Bivariate outliers

```{r, echo = FALSE, fig.align = "center", fig.width = 12, fig.height = 7}
par(mfrow = c(1, 3))
with(raw_data_clean, {
  plot(
    mpeso, maltura,
    pch = ifelse(id %in% outlier_weight_height_mother$id, 20, 1), 
    col = ifelse(id %in% outlier_weight_height_mother$id, "red", "black"),
    xlab = "Weight (kgs)",
    ylab = "Height (cms)",
    main = "Weight (kgs) by Height (cms)", 
    cex.main = 2, cex.lab = 1.5
  )
  plot(
    mpeso, mbraco,
    pch = ifelse(id %in% outlier_weight_muac_mother$id, 20, 1), 
    col = ifelse(id %in% outlier_weight_muac_mother$id, "red", "black"),
    xlab = "Weight (kgs)",
    ylab = "MUAC (cms)",
    main = "Weight (kgs) by MUAC (cms)", 
    cex.main = 2, cex.lab = 1.5
  )
  plot(
    maltura, mbraco,
    pch = ifelse(id %in% outlier_height_muac_mother$id, 20, 1), 
    col = ifelse(id %in% outlier_height_muac_mother$id, "red", "black"),
    xlab = "Height (cms)",
    ylab = "MUAC (cms)",
    main = "Height (cms) by MUAC (cms)", 
    cex.main = 2, cex.lab = 1.5
  )
})
```

```{r, echo = FALSE}
outlier_summary_bivariate_mother |>
  knitr::kable(
    col.names = c("Outlier type", "Number of records"),
    row.names = FALSE,
    caption = "Number of outliers per bivariate comparison"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, bold = TRUE, align = "center")
```

#### A total of **`r outlier_unique_bivariate_mother_total$n`** unique bivariate outliers were found and listed below. Potential outlier anthropometic measurements are in <strong><span style="color: red;" >BOLD RED</span></strong>.

```{r, echo = FALSE, eval = TRUE}
outlier_table_bivariate_mother |>
  dplyr::mutate(
    mweight = kableExtra::text_spec(
      x = mweight,
      format = "html",
      color = weight_outlier,
      bold = ifelse(weight_outlier == "red", TRUE, FALSE)
    ),
    mheight = kableExtra::text_spec(
      x = mheight,
      format = "html",
      color = height_outlier,
      bold = ifelse(height_outlier == "red", TRUE, FALSE)
    ),
    mmuac = kableExtra::text_spec(
      x = mmuac,
      format = "html",
      color = muac_outlier,
      bold = ifelse(muac_outlier == "red", TRUE, FALSE)
    )
  ) |>
  subset(select = c(today, id, ad2, ad3, mweight, mheight, mmuac)) |>
  knitr::kable(
    row.names = FALSE,
    col.names = c("Survey Date", "Record ID", "Survey Team", "Enum Code", 
                  "Weight (kgs)", "Height (cms)", "MUAC (cms)"),
    align = "r",
    caption = "Outliers based on statistical distance",
    escape = FALSE
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped", 
    full_width = FALSE, 
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, align = "center", bold = TRUE)
```

#### A total of **`r outlier_unique_mother_total$n`** unique outliers for mother anthropometric data were found. This is **`r outlier_unique_mother_total$p`** of the total dataset.

<br/>

## 2.2. Child anthropometry

&nbsp;

### 2.2.1. Check range and legal values

&nbsp;

#### Univariate

The boxplots below show the identified outliers for weight, height, and MUAC measurements.

```{r, echo = FALSE, eval = TRUE, fig.align = "center", fig.width = 12, fig.height = 5, fig.cap = "Outlier values for weight, height, and MUAC"}
plot_anthro_outliers(.data = raw_data_clean |> subset(age_months >= 6 & age_months < 60))
```

The number of outliers for each measurement are:

```{r, echo = FALSE}
outlier_summary_univariate |>
  knitr::kable(
    col.names = c("Outlier type", "Number of records"),
    row.names = FALSE,
    caption = "Number of outliers per measurement type"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, bold = TRUE, align = "center")
```

#### A total of **`r outlier_unique_univariate_total$n`** unique univariate outliers were found and listed below. Potential outlier anthropometric measurements are in <strong><span style="color: red;">BOLD RED</span></strong>.

```{r, echo = FALSE, eval = TRUE}
outlier_table_univariate |>
  dplyr::mutate(
    cweight = kableExtra::text_spec(
      x = cweight,
      format = "html",
      color = weight_outlier,
      bold = ifelse(weight_outlier == "red", TRUE, FALSE)
    ),
    cheight = kableExtra::text_spec(
      x = cheight,
      format = "html",
      color = height_outlier,
      bold = ifelse(height_outlier == "red", TRUE, FALSE)
    ),
    cmuac = kableExtra::text_spec(
      x = cmuac,
      format = "html",
      color = muac_outlier,
      bold = ifelse(muac_outlier == "red", TRUE, FALSE)
    ),
    flag = ifelse(flag == 1, "YES", "NO")
  ) |>
  subset(select = c(today, id, ad2, ad3, cweight, cheight, cmuac, age_months, flag)) |>
  knitr::kable(
    row.names = FALSE,
    col.names = c("Survey Date", "Record ID", "Survey Team", "Enum Code", 
                  "Weight (kgs)", "Height (cms)", "MUAC (cms)", "Age (months)", "Flagged in ODK"),
    align = "r",
    caption = "Outlier measurements - children",
    escape = FALSE
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped", 
    full_width = FALSE, 
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, align = "center", bold = TRUE)
```

When measurements are adjusted using the re-measured values, we get:

```{r, echo = FALSE}
outlier_summary_univariate_adj |>
  knitr::kable(
    col.names = c("Outlier type", "Number of records"),
    row.names = FALSE,
    caption = "Number of outliers per measurement type"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, align = "center", bold = TRUE)
```

#### A total of **`r outlier_unique_univariate_total_adj$n`** unique outliers were found and listed below. Potential outlier anthropometric measurements are in <strong><span style="color: red;" >BOLD RED</span></strong>.

```{r, echo = FALSE, eval = TRUE}
# xyz |>
outlier_table_univariate_adj |>
  dplyr::mutate(
    cweight1 = kableExtra::text_spec(
      x = cweight1,
      format = "html",
      color = weight_outlier,
      bold = ifelse(weight_outlier == "red", TRUE, FALSE)
    ),
    cheight1 = kableExtra::text_spec(
      x = cheight1,
      format = "html",
      color = height_outlier,
      bold = ifelse(height_outlier == "red", TRUE, FALSE)
    ),
    cmuac1 = kableExtra::text_spec(
      x = cmuac1,
      format = "html",
      color = muac_outlier,
      bold = ifelse(muac_outlier == "red", TRUE, FALSE)
    ),
    flag = ifelse(flag == 1, "YES", "NO")
  ) |>
  subset(select = c(today, id, ad2, ad3, cweight1, cheight1, cmuac1, age_months, flag)) |>
  knitr::kable(
    row.names = FALSE,
    col.names = c("Survey Date", "Record ID", "Survey Team", "Enum Code", 
                  "Weight (kgs)", "Height (cms)", "MUAC (cms)", "Age (months)", "Flagged in ODK"),
    align = "r",
    caption = "Outlier measurements (adjusted) - children",
    escape = FALSE
  )|>
  kableExtra::kable_styling(
    bootstrap_options = "striped", 
    full_width = TRUE, 
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, align = "center", bold = TRUE)
```

&nbsp;

#### Bivariate outliers

The scatterplots below identify various bivariate outliers.

```{r, echo = FALSE, eval = TRUE, fig.align = "center", fig.width = 12, fig.height = 5, fig.cap = "Bivariate outliers based on statistical distance"}
raw_data_clean |>
  subset(age_months >= 6 & age_months < 60) |>
  plot_anthro_bivariate(
    outlier_weight_height, 
    outlier_weight_muac, 
    outlier_height_muac, 
    outlier_weight_age, 
    outlier_height_age, 
    outlier_muac_age
  )
```

Following are the number of outliers identified per bivariate comparison.

```{r, echo = FALSE}
outlier_summary_bivariate |>
  knitr::kable(
    col.names = c("Outlier type", "Number of records"),
    row.names = FALSE,
    caption = "Number of outliers per bivariate comparison"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, align = "center", bold = TRUE)
```

#### A total of **`r outlier_unique_bivariate_total$n`** unique bivariate outliers are found and listed below. Potential outlier anthropometric measurements are in <strong><span style="color: red;">BOLD RED</span></strong>.

```{r, echo = FALSE, eval = TRUE}
outlier_table_bivariate |>
  dplyr::mutate(
    cweight = kableExtra::text_spec(
      x = cweight,
      format = "html",
      color = weight_outlier,
      bold = ifelse(weight_outlier == "red", TRUE, FALSE)
    ),
    cheight = kableExtra::text_spec(
      x = cheight,
      format = "html",
      color = height_outlier,
      bold = ifelse(height_outlier == "red", TRUE, FALSE)
    ),
    cmuac = kableExtra::text_spec(
      x = cmuac,
      format = "html",
      color = muac_outlier,
      bold = ifelse(muac_outlier == "red", TRUE, FALSE)
    ),
    flag = ifelse(flag == 1, "YES", "NO")
  )|>
  subset(select = c(today, id, ad2, ad3, cweight, cheight, cmuac, age_months, flag)) |>
  knitr::kable(
    row.names = FALSE,
    col.names = c("Survey Date", "Record ID", "Survey Team", "Enum Code", "Weight (kgs)", "Height (cms)", "MUAC (cms)", "Age (months)", "Flagged in ODK"),
    align = "r",
    caption = "Bivariate outliers based on statistical distance",
    escape = FALSE
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped", 
    full_width = TRUE, 
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, align = "center")
```

#### A total of **`r outlier_unique_total$n` outliers** were found. This is **`r outlier_unique_total$p`** of the full child anthropometric dataset.

&nbsp;

### 2.2.2. Flagged records

The anthropometric z-scores are calculated using the [`{zscorer}`](https://nutriverse.io/zscorer). Values are then assessed based on the WHO flagging criteria and problematic values are flagged. For this, we only use the data from children 6-59 months old and we first calculate z-score using the first measurements.

This produces an updated anthropometric dataset that now includes calculated anthropometric z-scores (weight-for-age, height-for-age, and weight-for-height) and identifies flagged values based on WHO flagging criteria and indicates which anthropometric measurement is potentially problematic.

Following are the flagged records in the anthropometric dataset. Anthropometric measurements with potential issues are in <strong><span style="color: red;" >BOLD RED</span></strong>.

```{r, eval = TRUE}
child_data_zscore |>
  dplyr::filter(
    flag_zscore != 0
    #flag_description != "No flagged measurements"#,
    #(cpeso != 0 | caltura != 0 | cbraco != 0)
  ) |>
  dplyr::mutate(
    weight_flag = ifelse(flag_zscore %in% c(2, 4, 6, 7), "red", "black"),
    height_flag = ifelse(flag_zscore %in% c(1, 2, 3, 7), "red", "black"),
    age_flag = ifelse(flag_zscore %in% c(1, 4, 5, 7), "red", "black"),
    cweight = kableExtra::text_spec(
      x = cweight,
      format = "html",
      color = weight_flag,
      bold = ifelse(weight_flag == "red", TRUE, FALSE)
    ),
    cheight = kableExtra::text_spec(
      x = cheight,
      format = "html",
      color = height_flag,
      bold = ifelse(height_flag == "red", TRUE, FALSE)
    ),
    age_months = kableExtra::text_spec(
      x = floor(age_months),
      format = "html",
      color = age_flag,
      bold = ifelse(age_flag == "red", TRUE, FALSE)
    ),
    flag = ifelse(flag == 1, "YES", "NO")
  ) |>
  subset(select = c(today, id, ad3, flag_description, flag, cweight, cheight, age_months)) |>
  knitr::kable(
    row.names = FALSE,
    col.names = c(
      "Survey Date", "Record ID", "Enum Code", "Flag Description", "Flagged in ODK", "Weight (kgs)", "Height (cms)", "Age (months)"
    ),
    caption = "Records with flagged anthropometric measurements based on WHO flagging criteria",
    escape = FALSE
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = TRUE,
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, align = "center")
```

A total of **`r flag_zscore_total`** records are identified. This is **`r flag_zscore_prop`** of the total records in the child anthropometric dataset.

Following are the flagged records in the anthropometric dataset after adjusting the measurements. Anthropometric measurements with potential issues are in <strong><span style="color: red;" >BOLD RED</span></strong>.

```{r, eval = TRUE}
child_data_zscore_adj |>
  dplyr::filter(
    flag_zscore != 0,
    #flag_description != "No flagged measurements",
    #(cpeso != 0 | caltura != 0 | cbraco != 0)
  ) |>
  dplyr::mutate(
    weight_flag = ifelse(flag_zscore %in% c(2, 4, 6, 7), "red", "black"),
    height_flag = ifelse(flag_zscore %in% c(1, 2, 3, 7), "red", "black"),
    age_flag = ifelse(flag_zscore %in% c(1, 4, 5, 7), "red", "black"),
    cweight = kableExtra::text_spec(
      x = cweight,
      format = "html",
      color = weight_flag,
      bold = ifelse(weight_flag == "red", TRUE, FALSE)
    ),
    cheight = kableExtra::text_spec(
      x = cheight,
      format = "html",
      color = height_flag,
      bold = ifelse(height_flag == "red", TRUE, FALSE)
    ),
    age_months = kableExtra::text_spec(
      x = round(age_months),
      format = "html",
      color = age_flag,
      bold = ifelse(age_flag == "red", TRUE, FALSE)
    ),
    flag = ifelse(flag == 1, "YES", "NO")
  ) |>
  subset(select = c(today, id, ad3, flag_description, flag, cweight, cheight, age_months)) |>  
  knitr::kable(
    row.names = FALSE,
    col.names = c("Survey Date", "Record ID", "Enum Code", "Flag Description", "Flagged in ODK", "Weight (kgs)", "Height (cms)", "Age (months)"
    ),
    caption = "Records with flagged anthropometric measurements based on WHO flagging criteria after measurement adjustment",
    escape = FALSE
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = TRUE,
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, align = "center")
```

A total of **`r flag_zscore_adj_total` child records** were flagged. This is **`r flag_zscore_adj_prop`** of the total records in the child anthropometric dataset.

&nbsp;

### 2.2.3. Distribution of anthropometric z-scores and MUAC

Removing outliers and flagged anthropometric measurements, we observe the distribution of the anthropometric z-scores and MUAC as follows:

```{r, echo = FALSE, eval = TRUE, fig.align = "center", fig.width = 12, fig.height = 5, fig.cap = "Distribution of anthropometric z-score values and MUAC"}
withr::with_par(
  new = list(par(mfrow = c(1, 4))),
  {
    with(
      child_data_zscore |>
        dplyr::filter(!id %in% c(outlier_table_univariate$id, outlier_table_bivariate$id) | flag_zscore == 0),
      {
        histNormal(wfaz, main = "Weight-for-age z-score", xlab = "z-score")
        histNormal(hfaz, main = "Height-for-age z-score", xlab = "z-score")
        histNormal(wfhz, main = "Weight-for-height z-score", xlab = "z-score")
        histNormal(cmuac, main = "MUAC", xlab = "cms")
      }
    )
  }
)
```

```{r, echo = FALSE, eval = TRUE, fig.align = "center", fig.width = 12, fig.height = 5, fig.cap = "Quantile-quantile plots of anthropometric z-score values and MUAC"}
withr::with_par(
  new = list(par(mfrow = c(1, 4))),
  {
    with(
      child_data_zscore |>
        dplyr::filter(!id %in% c(outlier_table_univariate$id, outlier_table_bivariate$id) | flag_zscore == 0),
      {
        qqNormalPlot(wfaz)
        qqNormalPlot(hfaz)
        qqNormalPlot(wfhz)
        qqNormalPlot(cmuac)
      }
    )
  }
)
```

&nbsp;

#### **Skewness and Kurtosis**

Checking for skewness and kurtosis on child anthropometric data, the following are observed:

**Skewness and kurtosis of weight-for-age z-score**

```{r, echo = FALSE, eval = TRUE}
skewKurt_wfaz
```

The skewness of weight-for-age z-score distribution is **<span style="color: blue">`r round(skewKurt_wfaz$s, digits = 0)`</span>**. This is **<span style="color: blue">`r skew_wfaz_class`</span>**.

The kurtosis of weight-for-age z-score distribution is **<span style="color: blue">`r round(skewKurt_wfaz$k, digits = 0)`</span>**. This is **<span style="color: blue">`r kurt_wfaz_class`</span>**.

**Skewness and kurtosis of height-for-age z-score**

```{r, echo = FALSE, eval = TRUE}
skewKurt_hfaz
```

The skewness of height-for-age z-score distribution is **<span style="color: blue">`r round(skewKurt_hfaz$s, digits = 0)`</span>**. This is **<span style="color: blue">`r skew_hfaz_class`</span>**.

The kurtosis of height-for-age z-score distribution is **<span style="color: blue">`r round(skewKurt_hfaz$k, digits = 0)`</span>**. This is **<span style="color: blue">`r kurt_hfaz_class`</span>**.

**Skewness and kurtosis of weight-for-height z-score**

```{r, echo = FALSE, eval = TRUE}
skewKurt_wfhz
```

The skewness of weight-for-height z-score distribution is **<span style="color: blue">`r round(skewKurt_wfhz$s, digits = 0)`</span>**. This is **<span style="color: blue">`r skew_wfhz_class`</span>**.

The kurtosis of weight-for-height z-score distribution is **<span style="color: blue">`r round(skewKurt_wfhz$k, digits = 0)`</span>**. This is **<span style="color: blue">`r kurt_wfhz_class`</span>**.

Checking for skewness and kurtosis on child anthropometric data where outliers and flagged values have been removed, the following are observed:

**Skewness and kurtosis of weight-for-age z-score - without outliers and flagged values**

```{r, echo = FALSE, eval = TRUE}
# skewKurt_wfaz_adj <- child_data_zscore |>
#     dplyr::filter(!id %in% c(outlier_table_univariate$id, outlier_table_bivariate$id) | flag_zscore == 0) |>
#     (\(x) skewKurt(x$wfaz))()
skewKurt_wfaz_adj
```

The skewness of weight-for-age z-score distribution is **<span style="color: blue">`r round(skewKurt_wfaz_adj$s, digits = 0)`</span>**. This is **<span style="color: blue">`r skew_wfaz_adj_class`</span>**.

The kurtosis of weight-for-age z-score distribution is **<span style="color: blue">`r round(skewKurt_wfaz_adj$k, digits = 0)`</span>**. This is **<span style="color: blue">`r kurt_wfaz_adj_class`</span>**.

**Skewness and kurtosis of height-for-age z-score - without outliers and flagged values**

```{r, echo = FALSE, eval = TRUE}
# skewKurt_hfaz_adj <- child_data_zscore |>
#     dplyr::filter(!id %in% c(outlier_table_univariate$id, outlier_table_bivariate$id) | flag_zscore == 0) |>
#     (\(x) skewKurt(x$hfaz))()
skewKurt_hfaz_adj
```

The skewness of height-for-age z-score distribution is **<span style="color: blue">`r round(skewKurt_hfaz_adj$s, digits = 0)`</span>**. This is **<span style="color: blue">`r skew_hfaz_adj_class`</span>**.

The kurtosis of height-for-age z-score distribution is **<span style="color: blue">`r round(skewKurt_hfaz_adj$k, digits = 0)`</span>**. This is **<span style="color: blue">`r kurt_hfaz_adj_class`</span>**.

**Skewness and kurtosis of weight-for-height z-score - without outliers and flagged values**

```{r, echo = FALSE, eval = TRUE}
# skewKurt_wfhz_adj <- child_data_zscore |>
#     dplyr::filter(!id %in% c(outlier_table_univariate$id, outlier_table_bivariate$id) | flag_zscore == 0) |>
#     (\(x) skewKurt(x$wfhz))()
skewKurt_wfhz_adj
```

The skewness of weight-for-height z-score distribution is **<span style="color: blue">`r round(skewKurt_wfhz_adj$s, digits = 0)`</span>**. This is **<span style="color: blue">`r skew_wfhz_adj_class`</span>**.

The kurtosis of weight-for-height z-score distribution is **<span style="color: blue">`r round(skewKurt_wfhz_adj$k, digits = 0)`</span>**. This is **<span style="color: blue">`r kurt_wfhz_adj_class`</span>**.

&nbsp;

### 2.2.4. Median absolute deviation of weight-for-height z-score

```{r, echo = FALSE, eval = TRUE}
if (whz_mad >= 0.8 & whz_mad <= 1.2) {
 mad_result <- "within the 0.8 to 1.2 range recommended."
} else {
  mad_result <- "NOT within the 0.8 to 1.2 range recommended."
}
```

The median absolute deviation (MAD) for weight-for-height z-score is **`r whz_mad`**. This is **`r mad_result`**.

&nbsp;

### 2.2.5. Digit preference

```{r, echo = FALSE, eval = TRUE, fig.align = "center", fig.width = 12, fig.height = 5, fig.cap = "Digit preference scores and plots for weight, height and MUAC"}
withr::with_par(
  new = list(par(mfrow = c(1, 3))),
  {
    with(child_data_zscore,
      {
        plot(dp_weight, cex.main = 2, cex.lab = 1.5)
        plot(dp_height, cex.main = 2, cex.lab = 1.5)
        plot(dp_muac, cex.main = 2, cex.lab = 1.5)
      }     
    )
  }
)
```

The **digit preference score for weight** is **`r dp_weight$dps`**. This digit preference score is **`r dp_weight$dpsClass`**.

The **digit preference score for height** is **`r dp_height$dps`**. This digit preference score is **`r dp_height$dpsClass`**.

The **digit preference score for MUAC** is **`r dp_muac$dps`**. This digit preference score is **`r dp_muac$dpsClass`**.

&nbsp;

### 2.2.6. Age heaping

```{r, echo = FALSE, eval = TRUE, fig.align = "center", fig.width = 8, fig.cap = "Plot assessing age heaping in the anthropometric dataset"}
plot(age_heaping)
```

```{r, echo = FALSE, eval = TRUE}
age_heaping

if (age_heaping$p < 0.05) {
  age_heaping_result <- "significant age heaping at whole years"
} else {
  age_heaping_result <- "no significant age heaping at whole years"
}
```

There is **`r age_heaping_result`** in the child anthropometric dataset.

&nbsp;

### 2.2.7. Sex ratio

The sex ratio in the anthropometric dataset is compared against the expected sex ratio of children under 5 years old in Mozambique which is 1.03 males for every female (from the [United States Census Bureau’s International Data Base](https://www.census.gov/data-tools/demo/idb/#/pop?COUNTRY_YEAR=2018&COUNTRY_YR_ANIM=2018&FIPS_SINGLE=MZ&menu=popViz&POP_YEARS=2018&quickReports=OVW&popPages=BYAGE&FIPS=MZ&ageGroup=5Y)).

```{r, echo = FALSE, eval = TRUE}
sex_ratio
```

```{r, echo = FALSE}
if (sex_ratio$p < 0.05) {
  sex_ratio_result <- "significantly different from the ratio of boys and girls in the general population"
} else {
  sex_ratio_result <- "not significantly different from the ratio of boys and girls in the general population"
}
```

The ratio of boys and girls in the data is **`r sex_ratio_result`** in Mozambique.

&nbsp;

### 2.2.8. Age ratio

```{r, echo = FALSE, eval = TRUE}
age_ratio
```

```{r, echo = FALSE}
if (age_ratio$p < 0.05) {
  age_ratio_result <- "significantly different from the expected age ratio of 0.85"
} else {
  age_ratio_result <- "not significantly different from the expected age ratio of 0.85"
}
```

The age ratio in the child anthropometric dataset is **`r age_ratio_result`**.

&nbsp;

### 2.2.9. Age structure

```{r, echo = FALSE, eval = TRUE, fig.align = "center", fig.width = 8, fig.height = 10, fig.cap = "Age structure of the under 5 sample"}
plot_age_structure(.data = raw_data_clean)
```


<br/>
<br/>