---
title: "Sofala Simple Spatial Survey Method (S3M)"
subtitle: "Survey Progress"
author: 
    - name: Mark Myatt
    - name: Ernest Guevarra
date: '`r Sys.time()`'
output: 
  html_document:
    toc: true
    toc_depth: 3
    self_contained: true
    code_download: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  error = FALSE,
  message = FALSE,
  echo = FALSE
)

suppressPackageStartupMessages(source("packages.R"))
for (f in list.files(here::here("R"), full.names = TRUE)) source (f)

targets::tar_load(
  c(raw_data, selected_ea_complete, complete_ea_sf,
    table_sp_total, table_sp_date_total, 
    table_team_total, table_team_date_total, check_ea_map, table_check_ea_map, 
    table_check_ea_out
  )
)
```

<style type="text/css">
  body{
  font-size: 14pt;
}
</style>

<br/>

# 1. Records by sampling point

&nbsp;

## 1.1. Number of records per sampling point as of `r Sys.time()`

```{r, echo = FALSE}
table_sp_total |>
  knitr::kable(
    row.names = FALSE,
    col.names = c("SP ID", "Number of records"),
    caption = "Number of records per SP ID"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(row = 0, bold = TRUE, align = "center") |>
  kableExtra::row_spec(
    row = nrow(table_sp_total) - 1, bold = TRUE, font_size = 28
  ) |>
  kableExtra::row_spec(
    row = nrow(table_sp_total), bold = TRUE, color = "red", font_size = 28
  ) |>
  kableExtra::row_spec(
    row = table_sp_total |> 
      head(nrow(table_sp_total) - 2) |> 
      (\(x) row.names(x)[!as.integer(x$Var1) %in% selected_ea_complete$spid])() |>
      as.integer(),
    bold = TRUE,
    color = "red"
  ) |>
  kableExtra::row_spec(
    row = table_sp_total |> 
      head(nrow(table_sp_total) - 2) |> 
      (\(x) x[as.integer(x$Var1) %in% selected_ea_complete$spid, ])() |> 
      (\(x) row.names(x)[x$Freq < 20])() |> 
      as.integer(),
    bold = TRUE,
    color = "blue"
  )
```

Sampling point identifiers in <strong><span style="color: red;" >BOLD RED are unrecognised/illegal values</span></strong> for this variable.

Sampling point identifiers in <strong><span style="color: blue;" >BOLD BLUE are sampling points with less than 20 records</span></strong>.

&nbsp;

## 1.2. Number of records by sampling point and by date

```{r, echo = FALSE}
table_sp_date_total |>
  knitr::kable(
    row.names = FALSE,
    caption = "Number of records by SP ID per day"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    font_size = 20,
    position = "center"
  ) |>
  kableExtra::row_spec(row = nrow(table_sp_date_total) - 1, bold = TRUE, font_size = 28) |>
  kableExtra::row_spec(row = nrow(table_sp_date_total), bold = TRUE, color = "red", font_size = 28) |>
  kableExtra::row_spec(
    row = table_sp_date_total |> 
      head(nrow(table_sp_date_total) - 2) |> 
      (\(x) (1:nrow(x))[!as.integer(x$`SP ID`) %in% selected_ea_complete$spid])(),
    bold = TRUE,
    color = "red"
  ) |>
  kableExtra::row_spec(
    row = table_sp_date_total |> 
      head(nrow(table_sp_date_total) - 2) |> 
      (\(x) x[as.integer(x$`SP ID`) %in% selected_ea_complete$spid, ])() |> 
      (\(x) (1:nrow(x))[x$`Total records by SP ID per day` < 20])(),
    bold = TRUE,
    color = "blue"
  ) |>
  kableExtra::row_spec(row = 0, bold = TRUE, align = "center")
```

Sampling point identiferis in <strong><span style="color: red;" >BOLD RED are unrecognised/illegal values</span></strong> for this variable.

Sampling point identifiers in <strong><span style="color: blue;" >BOLD BLUE are sampling points with less than 20 records</span></strong>.

&nbsp;

## 1.3. Survey teams recording incorrect sampling point identifiers

```{r, echo = FALSE}
x <- data.frame(
  table(
    raw_data$ad2[!raw_data$spid %in% selected_ea_complete$spid]
  )
) 

if (nrow(x) == 0) {
  cat("No survey teams have been recording incorrect sampling point identifiers")
} else {
  x |>
    (\(x) x[order(x$Freq), ])() |>
    (\(x) rbind(x, data.frame(Var1 = "Total", Freq = sum(x$Freq))))() 

  x |>
    knitr::kable(
      row.names = FALSE,
      col.names = c("Survey Team", "Number of records with incorrect SP ID")
    ) |>
    kableExtra::kable_styling(
      bootstrap_options = "striped",
      position = "center",
      full_width = FALSE,
      font_size = 20
    ) |>
    kableExtra::row_spec(row = nrow(x), bold = TRUE, font_size = 28)
}
```

&nbsp;

## 1.4. Map of records collected by enumeration area

```{r, echo = FALSE, eval = TRUE, fig.cap = "Map of records collected by enumeration area", fig.align = "center", out.width = "33%", fig.show = "hold"}
check_ea_map <- raw_data |>
  subset(!is.na(spid)) |>
  (\(x) x$ea_code)() |>
  (\(x) x[!is.na(c)])() |>
  unique() |>
  lapply(FUN = check_ea_geo, raw_data, complete_ea_sf)
```

We expect that the <strong><span style="color: darkgreen;">location of records (points in green)</span></strong> are within the <strong><span style="color: blue;">boundaries of the enumeration area</span></strong> in which they were reported to have been collected. If record locations are outside of these boundaries, there may be issues with the GPS recorded or the enumeration area selected.

```{r, echo = FALSE}
table_check_ea_map |>
  knitr::kable(
    row.names = FALSE,
    col.names = c(
      "Enumeration Area", "Records collected within EA", 
      "Records collected oustide EA", "Total Records"
    ),
    caption = "Number of records collected within appropriate enumeration area"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    font_size = 20,
    position = "center"
  ) |>
  kableExtra::row_spec(row = 0, bold = TRUE, align = "center") |>
  kableExtra::row_spec(
    row = table_check_ea_map |>
      (\(x) head(x, nrow(x) - 1))() |>
      (\(x) (1:nrow(x))[x$n_out > 0])(),
    bold = TRUE,
    color = "red"
  ) |>
  kableExtra::row_spec(
    row = nrow(table_check_ea_map), bold = TRUE, font_size = 28
  )
```

Enumeration areas in <strong><span style="color: red;" >BOLD RED are areas having records collected outside of the enumeration area</span></strong>.

A total of **`r table_check_ea_map$n_out[nrow(table_check_ea_map)]`** records were collected outside of the appropriate enumeration area.

Following are the records that have been collected outside of the appropriate enumeration areas.

```{r, echo = FALSE}
if (nrow(table_check_ea_out) == 0) {
  cat("No records have been recorded outside appropriate enumeration areas")
} else {
  table_check_ea_out |>
    knitr::kable(
      row.names = FALSE,
      col.names = c(
        "Record Identifier", "Survey Team", 
        "Enumerator Code", "Survey Date", "Enumeration Area"
      )
    ) |>
    kableExtra::kable_styling(
      bootstrap_options = "striped",
      position = "center",
      full_width = FALSE,
      font_size = 20
    ) |>
    kableExtra::row_spec(row = 0, bold = TRUE, align = "center")
}
```

<br/>

# 2. Records by survey team

&nbsp;

## 2.1. Number of records per survey team as of `r Sys.time()`

```{r, echo = FALSE}
table_team_total |>
  knitr::kable(
    row.names = FALSE,
    col.names = c("Survey Team", "Number of records"),
    caption = "Number of records per survey team"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(
    row = nrow(table_team_total), bold = TRUE, font_size = 28
  ) |>
  kableExtra::row_spec(row = 0, bold = TRUE, align = "center")
```

&nbsp;

## 2.2. Number of records per survey team per day as of `r Sys.time()`

```{r, echo = FALSE}
table_team_date_total |>
  knitr::kable(
    row.names = FALSE,
    caption = "Number of records per survey team per day"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center",
    font_size = 20
  ) |>
  kableExtra::row_spec(
    row = nrow(table_team_date_total), bold = TRUE, font_size = 28
  ) |>
  kableExtra::column_spec(
    column = ncol(table_team_date_total), bold = TRUE
  ) |>
  kableExtra::row_spec(row = 0, bold = TRUE, align = "center")
```

<br/>
<br/>



